# ART Co-op Initial Findings / Clean-up

```{r}
library(readr)
library(ggplot2)
library(ggpol)
library(plyr)
library(dplyr)
library(arsenal)
raw_data <- "https://raw.githubusercontent.com/AMPATH-Capstone/DataPrep/master/Original-Data/ARTcoops_SocialEconomic_01102020.csv" 
ampath_data <- read_csv(raw_data)
ampath_data[,7] <- ifelse(ampath_data[,7] == "Male", 1, ifelse(ampath_data[,7] == "Female", 0, NA))
ampath_data[,13] <- ifelse(ampath_data[,13] == "No School", 0, 
                           ifelse(ampath_data[,13] == "P1-P8", 1,
                                  ifelse(ampath_data[,13] == "S1-S4", 2,
                                          ifelse(ampath_data[,13] == "Tertiary/Vocational", 3,
                                                  ifelse(ampath_data[,13] == "University", 4, 
                                                                 ifelse(ampath_data[,13] == "Post-graduate", 5, 
                                                                 NA))))))
ampath_data

```

Identifying number of individuals who left the study
```{r}
total <- nrow(ampath_data)

study_id_count <- ampath_data %>%
  summarise(n_distinct(study_id))

total-(study_id_count * 2)

```


New subset with only individuals that left the study
```{r}
dropped_out <- ampath_data[!(duplicated(ampath_data$study_id) | duplicated(ampath_data$study_id, fromLast = TRUE)), ] 
dropped_out <- data.frame(dropped_out)
dropped_out
```

New data set without individuals who left the study
```{r}
completed_study <- anti_join(ampath_data, dropped_out)
completed_study <- data.frame(completed_study)
completed_study
```

Dropped out time to clinic (one-way in hours) & cost to travel to clinic
```{r}
timetoclinic_dropouts <- mean(dropped_out$time_to_hc_hr, na.rm=TRUE)
timetoclinic_dropouts

costtoclinic_dropouts <-  mean(dropped_out$cost_of_travel_to_hc, na.rm=TRUE)
costtoclinic_dropouts 

```
Completed study time to clinic (one-way in hours) & cost to travel to clinic
```{r}
timetoclinic_completed <- mean(completed_study$time_to_hc_hr, na.rm=TRUE)
timetoclinic_completed

costtoclinic_completed <-  mean(completed_study$cost_of_travel_to_hc, na.rm=TRUE)
costtoclinic_completed
```
Count of transportation for dropped out
```{r}
count(dropped_out, mode_of_transport_to_hc___1)
count(dropped_out, mode_of_transport_to_hc___2)
count(dropped_out, mode_of_transport_to_hc___3)
count(dropped_out, mode_of_transport_to_hc___4)
count(dropped_out, mode_of_transport_to_hc___5)
count(dropped_out, mode_of_transport_to_hc___6)
count(dropped_out, mode_of_transport_to_hc___7)
```


Mode to Clinic - for dropped out
```{r}
dropped_out_transportation <- data.frame( "Mode" = c(
  "Walking",
  "Own bicycle",
  "Boda-boda",
  "Matatu/bus",
  "Private vehicle / friend's vehicle",
  "Carried/assisted by somebody else",
  "Other"),
  "Count" = c(24,0,25,19,0,1,0)
)

dropped_out_transportation

```

Count of transportation for completed
```{r}
count(completed_study, mode_of_transport_to_hc___1)
count(completed_study, mode_of_transport_to_hc___2)
count(completed_study, mode_of_transport_to_hc___3)
count(completed_study, mode_of_transport_to_hc___4)
count(completed_study, mode_of_transport_to_hc___5)
count(completed_study, mode_of_transport_to_hc___6)
count(completed_study, mode_of_transport_to_hc___7)
```


Mode to Clinic - for completed
```{r}
completed_transportation <- data.frame( "Mode" = c(
  "Walking",
  "Own bicycle",
  "Boda-boda",
  "Matatu/bus",
  "Private vehicle / friend's vehicle",
  "Carried/assisted by somebody else",
  "Other"),
  "Count" = c(232,16,393,267,1,0,1)
)

completed_transportation
```


```{r}
completed_transportation$Status <- "Completed"
dropped_out_transportation$Status <- "Dropped Out"

transport <- rbind(completed_transportation, dropped_out_transportation)

ggplot(transport, aes(x=Mode, y=Count, fill=Status)) + 
  geom_bar(stat = "identity") +
  coord_flip()
```


