---
title: "Binary Logistic Regression & Stepwise_Regression"
author: "Kelsey Cooper"
date: "11/21/2020"
output: html_document
---

```{r}
library(mlbench)
library(MASS)
library(pROC)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(readr)
library(dplyr)

raw_data <- "https://raw.githubusercontent.com/AMPATH-Capstone/DataPrep/master/Original-Data/regression_data.csv" 
ampath_data <- read_csv(raw_data)

ampath_data$highest_school_level_hsm1 <-ifelse(ampath_data$highest_school_level_hsm1 == "No school", 0, 
                           ifelse(ampath_data$highest_school_level_hsm1 == "P1-P8", 1,
                                  ifelse(ampath_data$highest_school_level_hsm1 == "S1-S4", 2,
                                          ifelse(ampath_data$highest_school_level_hsm1 == "Tertiary/Vocational", 3,
                                                  ifelse(ampath_data$highest_school_level_hsm1 == "University", 4, 
                                                         ifelse(ampath_data$highest_school_level_hsm1 == "Post-graduate", 5, 
                                                                 NA))))))
```

Cleaned Table for Binary Logistic Regression for Control Group
```{r}
controlgroup<- ampath_data %>% 
      filter(redcap_event_name =='Initial' & participant_arm =='Control')
controlgroup <- na.omit(controlgroup)
controlgroup_new <- controlgroup[-c(1, 3:4)]
```

Summary of Binary Logistic Regression for Control Group
```{r}
logit_1 <- glm(droppedout~., family = binomial,data = controlgroup_new)
summary(logit_1)
```
Cleaned Table for Binary Logistic Regression for Intervention Group 
```{r}
interventiongroup<- ampath_data %>% 
      filter(redcap_event_name =='Initial' & participant_arm =='Intervention')
interventiongroup <- na.omit(interventiongroup)
interventiongroup_new <- interventiongroup[-c(1, 3:4)]
```

Summary of Binary Logistic Regression for Intervention Group 
```{r}
logit_2 <- glm(droppedout~., family = binomial,data = interventiongroup_new)
summary(logit_2)
```

AMPATH Data regardless of intervention or control group 
```{r}
ampath_data_new <- ampath_data[-c(1, 3:4)]
logit_3 <- glm(droppedout~., family = binomial,data = ampath_data_new)
summary(logit_3)
```

```{r}
library(stargazer)
stargazer(logit_1, logit_2, type="latex")
```

Stepwise Regression for Control Group 
```{r}
logit_4 <- stepAIC(logit_1)
```

```{r}
summary(logit_4)
```

Stepwise Regression for Intervention Group 
```{r}
logit_5 <- stepAIC(logit_2)
```

```{r}
summary(logit_5)
```

